{\it E}nKCF: Ensemble of Kernelized Correlation Filters for High-Speed, Object Tracking

### 2017-06-19 bmvc_review.tex
Revised the experimental section and went over the draft.

%----------------------------------------------------------------------
\section{Experiments} \label{sc:Experiments}
%---------------------------------------------------------------------- 
To evaluate the performance of the proposed algorithm, we choose two
publicly, available datasets:
OTB100 \footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
and
UAV123 \footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}.
The OTB100 dataset is comprised of the videos about 100 objects
whereas UAV123 dataset contains aerial footages of 123 objects. We aim
at developing an object tracking algorithm that ``efficiently'' runs
on an embedded system, a drone, for example, in ``high speed,'' $\ge
300$ fps. Given this, we believe that the UAV123 data is a good fit in
evaluating the performance of the proposed algorithm. In addition, in
the UAV123 data, there are many challenging, realistic scenes, e.g.,
abrupt scale/illumination changes. Although we are primarily
interested in developing an algorithm for mobile, embedded robotic
applications, it is also important to compare the performance of the
proposed algorithm with those of the state-of-the-art in a nominal
dataset for comparison. To this end, we chose the OTB100 data that
contains the videos recorded from smart phones and typical cameras in
perspective view. Lastly, we tested the proposed algorithm on a
temporally down-sampled version of the UAV123 dataset, called
UAV123$\_$10fps dataset. What we would like to see from this
experiment is to evaluate how robust the proposed algorithm is to
drastic motions of camera and targets.

\textbf{Finding Optimal Hyper-parameters} Each of three KCFs in {\it
  E}nKCF is designed for addressing specific challenges in single,
target tracking problem. Thus each of them should have different
values for the optimal parameters. For instance, the primary task of
the translation filter, $R_{t}^{L}$ is to estimate the translation of
a target from the previous frame whereas the scale filter, $R_{s}$ and
the estimated state of the particle filter are primarily used to
estimate the scale and translation. Because of this, we set the
learning rates ($\beta$) of individual filters, $R_{t}^{L}$,
$R_{t}^{S}$, and $R_{s}$ differently as $0.020$, $0.020$ and
$0.010$. For the kernel of the Gaussian neighboring function, we
empirically found the optimal values of $\alpha$ as $0.7$, $0.6$, and
$0.9$ for $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$. We set the scale
filter update threshold, $T_{R_{s}}$, to 4, peak-to-sidelobe (PSR)
ratio. Finally, the padding size for the correlation filters is tuned to $3$ for $R_{t}^{L}$, $2.50$ for $R_{t}^{S}$, 
and $1$ for $R_{s}$. For our particle filter implementation, we empirically set the
number of particles to $1000$ to balance the run-time performance and
accuracy. To keep the level of variance among the particles
reasonable, we performed the re-sampling only when the
\textit{efficient number of samples} ($ \hat{N}_{eff} \approx
(\sum_{p=1}^{P}w_{p}^{2})^{-1} $) is lower than a pre-defined
threshold.

\textbf{Features Selections} We used different features for each of
three KCFs as each of them has different goals to accomplish. In
particular, the translation filter, $R_{t}^{L}$, uses both the fast
Histograms of Oriented Gradients (fHoG) \cite{felzenszwalb2010object}
and color-naming \cite{van2009learning} features to learn the
background around the target more effectively. However we found,
through experiments, that only fHoG didn't work well to cover a larger
ROI. In a same way, we found that another translation filter,
$R_{t}^{S}$, worked well when it used fHoG features only and the scale
filter, $R_{s}$ did when it used both fHoG and color features.

\textbf{Performance on UAV123 Dataset} We compared, using the
precision and success rate metrics, the performance of the proposed
algorithm with those of the state-of-the-art high speed tracking
algorithms. For the precision, we rank the trackers based on the
precision numbers at 20 pixels whereas in the success rate plots,
trackers are ranked based on area under curve (AUC) scores. The
tracking algorithms under the comparison include ones in high-speed
($\geq$300 fps): KCF\cite{henriques2015high}, CSK
\cite{henriques2012exploiting}, DCF\cite{henriques2015high}, and
MOSSE\cite{bolme2010visual,henriques2015high} and ones in relatively
lower-speed ($\geq$50): SAMF\cite{li2014scale},
DSST\cite{danelljan2014accurate}, Struck\cite{hare2012efficient},
MUSTER \cite{hong2015multi}, TLD \cite{kalal2012tracking}, and OAB
\cite{zhang2012robust}. Figure \ref{fig:UAV123_DATASET} shows the
results on the UAV123 dataset. {\it E}nKCF outperformed most of the
high-speed tracking methods by $3\%$-$15\%$ in 20 pixels
precision. Three algorithms, SAMF, DSST, and Struck did about 5\%
better than ours in accuracy, but 10-20 times slower. For the scale
adaptation, {\it E}nKCF did second best in terms of AUC for the
success rate plot. It outperformed other tracking methods in
high-speed by about $20\%$-$25\%$ in AUC. In addition, it performed
even better than those algorithms that are slow, but a slightly better
in precision. For example, for AUC, {\it E}nKCF outperformed Struck
and DSST by $5\%$ and $10\%$ while running at more than $10$ and $30$
times faster.
\begin{figure}[!h]
\raggedright
\begin{tabular}{ccc}
\tiny\:\:\:\:\:\:\textbf{UAV123}\hspace{.44\linewidth}\:\:\:\textbf{OTB100}\\
\bmvaHangBox{\includegraphics[width=3.00cm]{./figures/pr_uav123.eps}}
\bmvaHangBox{\includegraphics[width=3.20cm]{./figures/sr_uav123.eps}}
\bmvaHangBox{\includegraphics[width=3.00cm]{./figures/pr_otb100.eps}}
\bmvaHangBox{\includegraphics[width=3.20cm]{./figures/sr_otb100.eps}}\\
\end{tabular}
\caption{Comparison of {\it E}nKCF's performance with other trackers on the UAV123 and OTB100 datasets.}
\label{fig:UAV123_DATASET}
\end{figure}

We also evaluate the performances of different combinations of the proposed correlation filters and 
compare them to {\it E}nKCF as shown in table~\ref{table:Comparison_to_LCT}.  
By using three KCFs ( $R_{t}^{L}$, $R_{t}^{S}$, $R_{s}$) in {\it E}nKCF,
we can achieve higher accuracy than using $R_{s}$ and $R_{t}^{L}$ or
$R_{t}^{S}$ with similar run-time performance. On the other hand, we
employ $R_{s}$ and $R_{t}^{L}$ or $R_{t}^{S}$ and run them in every frame in a similar way
to the multiple correlation filter framework of the LCT tracker \cite{ma2015long}. Running another filter, $R_{t}^{L}$ or
$R_{t}^{S}$, in the {\it E}nKCF framework not only boosts run-time performance but also increases
accuracy. Finally, we run  $R_{L}$, $R_{t}^{S}$ and $R_{s}$ in every frame in the in the given order. 
$R_{t}^{S}$ uses the translation estimation given by
$R_{t}^{L}$ to update translation and finally $R_{s}$ uses the final
translation estimation given by $R_{t}^{S}$ to update the
scale. Interestingly, running two complementary translation filter
results in significant improvement at the cost of decreased run-time
performance. In conclusion, running two complementary translation
filter and a scale filter in the {\it E}nKCF framework not only
provides high speed but also more accurate tracker than the baseline
methods having one translation and one scale filter.
\begin{table}[!h]
\smaller
\begin{center}
\color{green}--- Best \hspace{.15\linewidth}\color{red}--- $2^{nd}$ Best \hspace{.15\linewidth}\color{blue}--- $3^{th}$ Best \color{black}\\
\resizebox{\textwidth}{!}{\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|}
\hline
Method & {\it E}nKCF & $R_{t}^{S}$+$R_{t}^{L}$+$R_{s}$ & $R_{t}^{L}$+$R_{s}$ & $R_{t}^{S}$+$R_{s}$ & $R_{t}^{L}$* & $R_{t}^{S}$* & $R_{t}^{L}$+$R_{s}$* & $R_{t}^{S}$+$R_{s}$* & $R_{t}^{L}+R_{t}^{S}$+$R_{s}$* \\
\hline\hline
Pr. ($20$px) & \color{blue}53.9 & 48.93 &52.41 & 48.10 & 51.88 & 51.29 & \color{red} 55.85 & 52.14 & \color{green}58.16 \\
SR ($50\%$) & \color{red} 40.2 & 36.75 & 38.23 & 36.04 & 35.12 & 34.43 & \color{blue}39.89 & 38.51 & \color{green}41.58 \\
FPS & \color{red} 416 & \color{blue}412 & 370 & \color{green}425 & 365 & 384 & 135 & 151 & 99 \\
\hline
\end{tabular}}
\end{center}
\caption{Evaluations of the different combinations of the proposed
  KCFs in UAV123 dataset. The particle filter is decoupled from all the methods for fair comparison. 
  The $2^{nd}$ method swaps the order of
  $R_{t}^{L}$ and $R_{t}^{S}$ (fig.~\ref{Workflows}). The $3^{th}$
  method removes $R_{t}^{S}$ and replaces with $R_{t}^{L}$ whereas the
  $3^{th}$ one removes $R_{t}^{L}$. The methods denoted with "*" run
  the filters in every frame in the listed order. The LCT tracker
  \cite{ma2015long} runs a translation and scale filter in every frame
  (similar to $6^{th}$ method) and couples a re-detection method to
  perform long-term tracking at $\approx30$ fps.}
\label{table:Comparison_to_LCT}
\end{table}

Finally, on the $UAV123$ dataset, we compare the {\it E}nKCF with particle filter to the one without particle filter. To do so, we use 50 sequences labeled as no abrupt camera motion in the dataset. To evaluate the robustness of particle filter, we add noise, drawn from a uniform distribution ($[-20,20]$), to the translation estimations of the KCFs. In these settings, the {\it E}nKCF with particle filter achieves $51.98\%$ precision ($20$px), outperforming the baseline {\it E}nKCF by $6.32\%$.  In conclusion, with the removal of global camera motion, the integration of particle filter into the {\it E}nKCF as shown in fig.~\ref{Workflows} can further improve the results.

>>>>

%----------------------------------------------------------------------
\section{Experiments} \label{sc:Experiments}
%---------------------------------------------------------------------- 
To evaluate the performance of the proposed algorithm, we choose two
publicly, available datasets:
OTB100 \footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
and
UAV123 \footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}.
The OTB100 dataset is comprised of the videos about 100 objects
whereas UAV123 dataset contains aerial footages of 123 objects. We aim
at developing an object tracking algorithm that ``efficiently'' runs
on an embedded system, a drone, for example, in ``high speed,'' $\ge
300$ fps. Given this, we believe that the UAV123 data is a good fit in
evaluating the performance of the proposed algorithm. In addition, in
the UAV123 data, there are many challenging, realistic scenes, e.g.,
abrupt scale/illumination changes. Although we are primarily
interested in developing an algorithm for mobile, embedded robotic
applications, it is also important to compare the performance of the
proposed algorithm with those of the state-of-the-art in a nominal
dataset for comparison. To this end, we chose the OTB100 data that
contains the videos recorded from smart phones and typical cameras in
perspective view. Lastly, we tested the proposed algorithm on a
temporally down-sampled version of the UAV123 dataset, we call it
UAV123$\_$10fps dataset. What we would like to evaluate using this
modified dataset is how robust the proposed algorithm is to the
drastic motions of camera and targets.

\textbf{Finding Optimal Hyper-parameters} Each of three KCFs in {\it
  E}nKCF is designed to address specific challenges in single, target
tracking problem. Thus each of them should have different values for
the optimal parameters. For instance, the primary task of the
translation filter, $R_{t}^{L}$ is to estimate the translation of a
target from the previous frame whereas the scale filter, $R_{s}$ and
the estimated state of the particle filter are primarily used to
estimate the scale and translation. Because of this, we set the
learning rates ($\beta$) of individual filters, $R_{t}^{L}$,
$R_{t}^{S}$, and $R_{s}$ differently as $0.020$, $0.020$ and
$0.010$. For the kernel of the Gaussian neighboring function, we
empirically found the optimal values of $\alpha$ as $0.7$, $0.6$, and
$0.9$ for $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$. We set the scale
filter update threshold, $T_{R_{s}}$, to 4, peak-to-sidelobe (PSR)
ratio. Finally, the padding size for the correlation filters is tuned
to $3$ for $R_{t}^{L}$, $2.50$ for $R_{t}^{S}$, and $1$ for
$R_{s}$. For our particle filter implementation, we empirically set
the number of particles to $1000$ to balance the run-time performance
and accuracy. To keep the level of variance among the particles
reasonable, we performed the re-sampling only when the
\textit{efficient number of samples} ($ \hat{N}_{eff} \approx
(\sum_{p=1}^{P}w_{p}^{2})^{-1} $) is lower than a pre-defined
threshold.

\textbf{Features Selections} We used different features for each of
three KCFs as each of them has different goals to accomplish. In
particular, the translation filter, $R_{t}^{L}$, uses both the fast
Histograms of Oriented Gradients (fHoG) \cite{felzenszwalb2010object}
and color-naming \cite{van2009learning} features to more effectively
learn the background around the target. Through experiments, we found
that only fHoG didn't work well to cover a larger ROI; another
translation filter, $R_{t}^{S}$, worked well when it used fHoG
features only; the scale filter, $R_{s}$ did when it used both fHoG
and color features.

\textbf{Performance on UAV123 Dataset} We used the precision and
success rate metrics to compare the performance of the proposed
algorithm with those of the state-of-the-art high speed tracking
algorithms. For the precision, we rank the trackers based on the
precision numbers at 20 pixels whereas in the success rate plots,
trackers are ranked based on area under curve (AUC) scores. The
tracking algorithms under the comparison include ones in high-speed
($\geq$300 fps): KCF \cite{henriques2015high}, CSK
\cite{henriques2012exploiting}, DCF \cite{henriques2015high}, and
MOSSE \cite{bolme2010visual,henriques2015high} and ones in relatively
lower-speed ($\geq$50): SAMF \cite{li2014scale}, DSST
\cite{danelljan2014accurate}, Struck \cite{hare2012efficient}, MUSTER
\cite{hong2015multi}, TLD \cite{kalal2012tracking}, and OAB
\cite{zhang2012robust}. Figure \ref{fig:UAV123_DATASET} shows the
results on the UAV123 dataset. {\it E}nKCF outperformed most of the
high-speed tracking methods by $3\%$-$15\%$ at 20 pixels
precision. Three algorithms, SAMF, DSST, and Struck did about 5\%
better than ours in accuracy, but 10-20 times slower. For the scale
adaptation, {\it E}nKCF did second best in terms of AUC for the
success rate plot. It outperformed other tracking methods in
high-speed by about $20\%$-$25\%$ in AUC. In addition, it performed
even better than those algorithms that are slow, but a slightly better
in precision. For example, for AUC, {\it E}nKCF outperformed Struck
and DSST by $5\%$ and $10\%$ while running at more than $10$ and $30$
times faster.
\begin{figure}[!h]
\raggedright
\begin{tabular}{ccc}
\tiny\:\:\:\:\:\:\textbf{UAV123}\hspace{.44\linewidth}\:\:\:\textbf{OTB100}\\
\bmvaHangBox{\includegraphics[width=3.00cm]{./figures/pr_uav123.eps}}
\bmvaHangBox{\includegraphics[width=3.20cm]{./figures/sr_uav123.eps}}
\bmvaHangBox{\includegraphics[width=3.00cm]{./figures/pr_otb100.eps}}
\bmvaHangBox{\includegraphics[width=3.20cm]{./figures/sr_otb100.eps}}\\
\end{tabular}
\caption{Comparison of {\it E}nKCF's performance with other trackers on the UAV123 and OTB100 datasets.}
\label{fig:UAV123_DATASET}
\end{figure}

Table \ref{table:Comparison_to_LCT} presents the performance of
different combinations of the proposed algorithm. In short, we
empirically verified that \textit{E}nKCF is an optimal combination in
terms of tracking accuracy and run-time performance. We could achieve
4.26\% higher in accuracy by running $R_{R}^{t}$ and $R_{S}$ at every
frame, but this combination wills sacrifice run-time performance 317
fps.  To be more specific, we employ $R_{s}$ and $R_{t}^{L}$ or
$R_{t}^{S}$ to run them in every frame in a similar way to the
multiple correlation filter framework of the LCT tracker
\cite{ma2015long}. Running another filter, $R_{t}^{L}$ or $R_{t}^{S}$,
in the {\it E}nKCF framework not only boosts run-time performance but
also increases accuracy. Lastly, we run $R_{L}$, $R_{t}^{S}$ and
$R_{s}$ in every frame.  $R_{t}^{S}$ uses the translation estimated by
$R_{t}^{L}$ to update translation and $R_{s}$ uses the final
translation estimation given by $R_{t}^{S}$ to update the
scale. Interestingly, running two complementary translation filter
results in significant improvement at the cost of decreased run-time
performance. In summary, running two (complementary) translation
filters and a scale filter as {\it E}nKCF not only increases run-time
performance but also offers more accurate tracker than the baseline
method with one translation and one scale filter.
\begin{table}[!h]
\smaller
\begin{center}
\color{green}--- Best \hspace{.15\linewidth}\color{red}--- $2^{nd}$ Best \hspace{.15\linewidth}\color{blue}--- $3^{th}$ Best \color{black}\\
\resizebox{\textwidth}{!}{\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|}
\hline
Method & {\it E}nKCF & $R_{t}^{S}$+$R_{t}^{L}$+$R_{s}$ & $R_{t}^{L}$+$R_{s}$ & $R_{t}^{S}$+$R_{s}$ & $R_{t}^{L}$* & $R_{t}^{S}$* & $R_{t}^{L}$+$R_{s}$* & $R_{t}^{S}$+$R_{s}$* & $R_{t}^{L}+R_{t}^{S}$+$R_{s}$* \\
\hline\hline
Pr. ($20$px) & \color{blue}53.9 & 48.93 &52.41 & 48.10 & 51.88 & 51.29 & \color{red} 55.85 & 52.14 & \color{green}58.16 \\
SR ($50\%$) & \color{red} 40.2 & 36.75 & 38.23 & 36.04 & 35.12 & 34.43 & \color{blue}39.89 & 38.51 & \color{green}41.58 \\
FPS & \color{red} 416 & \color{blue}412 & 370 & \color{green}425 & 365 & 384 & 135 & 151 & 99 \\
\hline
\end{tabular}}
\end{center}
\caption{Evaluations on different combinations of the KCFs for UAV123
  dataset. We removed the particle filter from this experiment. The
  $2^{nd}$ method fliped the way of deploying $R_{t}^{L}$ and
  $R_{t}^{S}$ (fig.~\ref{Workflows}). The $3^{th}$ method removed
  $R_{t}^{S}$ and replaces with $R_{t}^{L}$ whereas the $3^{th}$ one
  removes $R_{t}^{L}$. {\it Burak: $3^{th}$ and $3^{th}$?} The methods
  marked with "*" run the filters on every frame in the listed
  order. The LCT tracker \cite{ma2015long} runs a translation and
  scale filter in every frame (similar to the method at the $6^{th}$
  column {\it Burak: Not in $7^{th}$?} and couples a re-detection
  method to perform long-term tracking at $\approx30$ fps.}
\label{table:Comparison_to_LCT}
\end{table}

For the $UAV123$ dataset, we also evaluated the performance of the
{\it E}nKCF with and without the particle filter. In particular, we
use 50 sequences labeled as no abrupt camera motion in the dataset. To
evaluate the robustness of particle filter, we add noise, drawn from a
uniform distribution ($[-20,20]$), to the translation estimations of
the KCFs. In these settings, the {\it E}nKCF with particle filter
achieves $51.98\%$ precision ($20$px), outperforming the baseline {\it
  E}nKCF by $6.32\%$. {\it Burak: the baseline here is the one without
  particle filter?} In summary, with the removal of global camera
motion, the integration of particle filter into the {\it E}nKCF as
shown in fig.~\ref{Workflows} further improved the results.
